
Practical Machine Learning /Course Project: Writeup
====================================================

##Summary

The aim of this report is the describe the steps and results of building models and predicting the "classe" variable. 



##Steps

* Reading training and testing data set in

```{r}
test<-read.csv("pml-testing.csv")
train<-read.csv("pml-training.csv")
```

* Splitting training dataset into training and testing set (60/40) 

```{r}
library(caret)
library(kernlab)
trainIndex <- createDataPartition(train$classe, p = 0.60)[[1]]
training = train[trainIndex,]
testing = train[-trainIndex,]
```

* Creating 3 different models (forarm, belt, and arm) on the basis of cross-validation

```{r}
modelforarm<-train(classe ~gyros_forearm_x+gyros_forearm_y+gyros_forearm_z+accel_forearm_x+accel_forearm_y+accel_forearm_z+magnet_forearm_x+magnet_forearm_y+magnet_forearm_z, data=training, trControl = trainControl(method = "cv"))
predictedforarm <- predict(modelforarm, newdata=testing)
confusionMatrix(predictedforarm, testing$classe)

modelbelt<-train(classe ~gyros_belt_x+gyros_belt_y+gyros_belt_z+accel_belt_x+accel_belt_y+accel_belt_z+magnet_belt_x+magnet_belt_y+magnet_belt_z, data=training, trControl = trainControl(method = "cv"))

modelarm<-train(classe ~gyros_arm_x+gyros_arm_y+gyros_arm_z+accel_arm_x+accel_arm_y+accel_arm_z+magnet_arm_x+magnet_arm_y+magnet_arm_z, data=training, trControl = trainControl(method = "cv"))
```

* Calculating accuracy of the 3 models (Forarm, Belt, Arm)

** Forarm
```{r}
predictedforarm <- predict(modelforarm, newdata=testing)
confusionMatrix(predictedforarm, testing$classe)
```

** Belt
```{r}
predictedbelt <- predict(modelbelt, newdata=testing)
confusionMatrix(predictedbelt, testing$classe)
```

** Arm
```{r}
predictedarm <- predict(modelarm, newdata=testing)
confusionMatrix(predictedarm, testing$classe)
```
##Conclusion

My models could predict the classe variable with ca. 0.7 - 0.8 accuracy.

I have selected these models because the moving of these body parts during the exercises could definitely affect the quality of the exercises.

